Commutative Character Sheaves

### 2015-11-15 followup.tex
Added review and proposition to Section 4. But it's very rough, still.
I need to put this down for a few hours.

\begin{proof}
Let $\Delta$ be the image of the boundary homomorphism $\delta$ in the sequence
\[
1 \to G\der(k) \to G(k) \to G\ab(k) \xrightarrow{\delta} \Hh^1(k, G\der),
\]
yielding a short exact sequence
\[
1 \to G(k) / G\der(k) \to G\ab(k) \to \Delta \to 1.
\]
Applying $\Hom(-, \EEx)$ and using the fact that every homomorphism $G(k) \to \EEx$ vanishes on $G\der(k)$, we get
\[
1 \to \Delta^* \to G\ab(k)^* \to G(k)^* \to 1.
\]
By Theorem~\ref{thm:Gab}, the trace of Frobenius map 
\end{proof}

\begin{proposition}
Every map in $\CCS(G)$ is either trivial or an isomorphism. 
For every commutative character sheaf on $G$, its automorphism group is
$
\Hh^1(\pi_0(G\ab),\EEx)^{\Frob{}}.
$
\end{proposition}

\begin{proof}
$= \Aut_{\CCS(G\ab)}(\cs{L}\ab,\mu\ab) =$
\end{proof}

@@

@@

\section{Applications}

\subsection{Linear Characters}

\begin{proposition}
Let $(\underline{G}(\OK),\rho)$ be a type such that  . . . 
Set $G = \Gr(\underline{G})$.
There is a virtual admissible $\ell$-adic sheaf $\mathcal{F}$ on $G$ such that $\trFrob{\mathcal{F}} = \trace \rho$ under the canonical isomorphism $G(\Fq) \iso \underline{G}(\OK)$.
\end{proposition}

It is not unique.

As proved in \cite{kim:07a}, many (complex) supercuspidal representations of $p$-adic groups can be built from the generic data of \cite{yu:01a}*{\S 15} and, moreover, the type (in the sense of \cite{bushnell-kutzko:98a}) of the resulting supercuspidal representations can be constructed directly from the generic data. 
Let us refer to the types arising in this manner as {\it generic types}.
In this section we show that, after fixing an isomorphism $\CC \approx \EE$, every generic type is geometrizable, in the sense that every part of generic type admits a description as a perverse sheaf, from which the type can be recovered.

>>>>

\begin{proof}
Let $\Delta$ be the image of the boundary homomorphism $\delta$ in the sequence
\[
1 \to G\der(k) \to G(k) \to G\ab(k) \xrightarrow{\delta} \Hh^1(k, G\der),
\]
yielding a short exact sequence
\[
1 \to G(k) / G\der(k) \to G\ab(k) \to \Delta \to 1.
\]
Applying $\Hom(-, \EEx)$ and using the fact that every homomorphism $G(k) \to \EEx$ vanishes on $G\der(k)$, we get
\[
1 \to \Delta^* \to G\ab(k)^* \to G(k)^* \to 1.
\]
By Theorem~\ref{thm:Gab}, the trace of Frobenius map  . . . .\todo{Finish this.}
\end{proof}

\begin{remark}
Note that when $\Hh^1(k,G\der) = 0$, as is the case when $G\der(\bFq)$ ``is simply connected,'' then $\CCSiso{G} \iso G(\Fq)^*$, so
we succeed in geometrizing characters of $G(k)$ on the nose.
\end{remark}

\begin{proposition}
Every map in $\CCS(G)$ is either trivial or an isomorphism. 
For every commutative character sheaf on $G$, its automorphism group is
$
((\pi_0(G\ab))^*)^{\Frob{}}.
$
\end{proposition}

\begin{proof}
By Theorem~\ref{thm:Gab}, $\Aut_{\CCS(G)}(\cs{L},\mu,\beta) = \Aut_{\CCS(G\ab)}(\cs{L}\ab,\mu\ab)$. 
By \cite{cunningham-roe:13a}*{Thm 3.9},  $\Aut_{\CCS(G\ab)}(\cs{L}\ab,\mu\ab) = ((\pi_0(G\ab))^*)^{\Frob{}}$.
\end{proof}

@@

\section{Application to type theory for $p$-adic groups}

\iffalse
\subsection{Linear Characters}

\newcommand{\red}{^{\operatorname{red}}}

As proved in \cite{kim:07a}, many (complex) supercuspidal representations of $p$-adic groups can be built from the generic data of \cite{yu:01a}*{\S 15} and, moreover, the type (in the sense of \cite{bushnell-kutzko:98a}) of the resulting supercuspidal representations can be constructed directly from the generic data. 
Let us refer to the types arising in this manner as {\it generic types}.
In this section we show that every generic type is geometrizable, in a sense which will be made clear below.

\subsection{Review of Yu's types}

\begin{quotation}
Therefore, up to some linear characters, all the ingredient representations are on groups of
 the form $H(\mathcal{O})$, where $H$ is a smooth group scheme over $\mathcal{O}$, and the representations are inflated $H(\kappa)$. These results suggest that algebraic geometry and group schemes should play an
  from $H$
important role in the representation theory of p-adic groups.
\end{quotation}

\subsection{Smooth group schemes for types}

Let $\underline{G}$ be an affine smooth group scheme of finite type over $\OK$ arising in the work of Yu on types for supercuspidal groups.
We suppose the component group $\pi_0(\underline{G}_s\red)$ of the reductive quotient of the special fibre $\underline{G}_s$ of $\underline{G}$ is cyclic.

The group scheme $\underline{G}$ comes equipped with affine smooth group schemes of finite type over $\OK$
\[
\underline{J}^i \to \underline{G},
\]
for $j=0, 1, \ldots , d-1,d$, such that
\[
\underline{G}(\OK) = \prod_{i=0}^{d} \underline{J}^i(\OK).
\]
Let $\underline{G}^{j-1}$ be the canonical smooth model . . 
We suppose the component group $\pi_0((\underline{G}^{j-1}_s)\red)$ of the reductive quotient of the special fibre $\underline{G}^{j-1}_s$ of $\underline{G}^{j-1}$ is cyclic, for every $j=1, \ldots, d-1$.

\subsection{Geometrization of types}

\begin{proposition}
Let $(\underline{G}(\OK),\tau)$ be a type such that  . . . 
Set $G = \Gr(\underline{G})$.
There is a virtual admissible $\ell$-adic sheaf $\mathcal{F}$ on $G$ such that $\trFrob{\mathcal{F}} = \trace \tau$ under the canonical isomorphism $G(\Fq) \iso \underline{G}(\OK)$.
\end{proposition}

\begin{proof}
Now, let $(A,\varphi)$ be a Frobenius-stable character sheaf on $\underline{G}_s\red$.
Let $(A,\varphi)$ be the Frobenius-stable constructible sheaf on $\underline{G}_s$ obtained by pull-back.
For each $j=1,\ldots, d-1$, 
let $(A^j, \varphi^j)$ be a character sheaf on $(\underline{G}^{j-1}_s)\red$, in the sense of [Lusztig, CSDG].
Let $(C_1^j, \phi^j)$ be the Frobenius-stable constructible sheaf on $\underline{G}^{j-1}_s$ obtained by pull-back..

For each $j=1,\ldots, d-1$,
let $H^j$ be a unipotent group appearing as a quotient $\underline{J}^j_s \to H^j$.
Let $B^j$ be a character sheaf on $H^j$, in the sense of [Boyarchenko].
Let $(D_1^j,\varphi^j)$ be the Frobenius-stable constructible sheaf on $\underline{J}^{j}_s$ obtained by pull-back.

Let $n$ be a positive integer and
for each $j=1,\ldots, d-1$, let $\cs{L}_n^{j-1}$ be a commutative quasicharacter sheaf on $G_n^{j-1}\ceq \Gr_n(\underline{G}^{j-1})$.

Observe that $\underline{G}^{j-1}_s = \Gr_1(\underline{G}^{j-1})$ 
and $\underline{J}^{j}_s = \Gr_1(\underline{G}^{j-1})$. 
Let $(\cs{C}_n^j,\phi^j)$ be the admissible sheaf on $G_n^{j-1} \ceq \Gr_n(\underline{G}^{j-1})$ obtained by pulling-back $C_1$ along $G_n^{j-1} \to \underline{G}^{j-1}_s$.
Let $(\cs{D}_n^j,\phi^j)$ be the admissible sheaf on $J_n^{j-1} \ceq \Gr_n(\underline{J}^{j-1})$ obtained by pull-back along $J_n^{j-1} \to \underline{J}^{j-1}_s$.

Set $\underline{N}^j = \prod_{i=j}^d \underline{J}^i$ and let $\underline{G} \to \underline{M}^j$ be the morphism . . . .
Then $\underline{M}^j = \underline{G}^{j-1} \underline{J}^j$ . . . 
%
Now, consider the following sheaf on $M_n^j \ceq \Gr_n(\underline{M}^j)$:
\[
\cs{E}_n^j \ceq (\cs{L}_n^{j-1}\otimes \cs{C}_n^j) \boxtimes \cs{D}_n^{j}
\]
Let $\cs{F}_n^j$ be the pullback along $G_n :=\Gr_n(\underline{G}) \to \Gr_n(\underline{M}^j):= M_n^j$.
Finally, set $\cs{F}_n = \otimes_i \cs{F}^i_n$.

\end{proof}

@@
